SBML L3 paper response to reviewers

### 2020-01-01 main.tex
Fiddling with formatting

\hspace{4in}%

\vspace*{2ex}

@@

@@

With kind regards,\\
Michael Hucka, Dagmar Waltemath, Sarah Keating, Matthias K\"{o}nig, Claudine Chaouiya, Andreas Dr\"{a}ger, Fengkai Zhang, and Chris Myers, on behalf of all the coauthors.

\vspace*{2em}

>>>>

\vspace*{4em}

\hspace{4.1in}\today

\vspace*{1em}

@@

\vspace*{1em}

@@

\vspace*{1em}
\hspace{4in}
\begin{minipage}{3in}
With kind regards,\\
\\[1ex]
Michael Hucka\\
Dagmar Waltemath\\
Sarah Keating\\
Matthias K\"{o}nig\\
Claudine Chaouiya\\
Andreas Dr\"{a}ger\\
Fengkai Zhang\\
Chris Myers\\
on behalf of all the coauthors.
\end{minipage}

\clearpage

\begin{center}
\large Summary of changes
\end{center}
